---
title: "ROC Report"
author: "Jeff Gould"
date: "7/7/2020"
output: 
  html_document:
    md_extensions: +raw_html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(plotly)
library(mgcv)

source("ROC_functions.R")
teams_colors_logos <- readRDS("teams_colors_logos.rds")
pbp_all <- readRDS("pbp_all.rds") %>% distinct() %>% filter(season == 2019, week %in% c(1:16))
source("theme_CC.R")
```

## Receiver Opportunity Composite Score (ROC Score)

The ROC Score is a Contested Catch metric that was built using NFL play-by-play data to better predict WR fantasy scoring over the course of a season. It is an in-season tool, designed to be used over a 4-5 game window to predict fantasy scoring over the next 3-5 weeks. Right now we show a static ROC report over the course of the 2019 season, weeks 1-16, but once the 2020 season begins we will update this page weekly.

Additionally, we have a fully interactive [app available here](htps://contestedcatch.shinyapps.io/ROC_app) for more detailed analysis and data research.


```{r message=FALSE, warning=FALSE, fig.width=12, fig.height=9}
ROC_data <- make_ROC(pbp_data = pbp_all, weeks = c(1:16), positions = c("WR", "TE", "RB", NA),
                                szn = 2019, reception_min = 25)

ggplot(ROC_data %>% rename(Receiver = receiver) %>% filter(Receptions >= 50), 
                              aes(x = ROC, y = fantasy_points, label1 = TargetShare, 
                                  label2 = Targets,
                                  label3 = PlayerAirYards, 
                                  label4 = AirYardShare, 
                                  label5 = Receiver,
                                  label6 = season)) +
                         geom_point(aes(color = posteam), show.legend = F) +
                         scale_color_manual(values = teams_colors_logos$team_color, breaks = teams_colors_logos$team_abbr) +
                         scale_x_continuous(limits = c(0,max(100, max(ROC_data$ROC))), breaks = seq(0,200,20)) +
                         labs(y = "0.5 PPR Fantasy Receiving Points", 
                              title = "Contested Catch: Receiver Opportunity Composite (ROC Score)", 
                              x = "ROC Score") +
                         theme_CC() +
  ggrepel::geom_text_repel(aes(label = Receiver))


get_ROC_buys(ROC_data, c(1:16))

get_ROC_sells(ROC_data, c(1:16))

ROC_table(ROC_data, "All") %>% kable() %>%
  kable_styling(c("striped", "hover"), full_width = F)


```
